Identifying regime transitions for water governance at a basin scale

### 2022-04-26 paper/main/04_discussion.tex
docs(abstract,-introduction,-results,-discussion): fit to the new structure and results
BREAKING CHANGE:

\begin{figure*}[htbp!]
	\centering
	\includegraphics[width=0.9\linewidth]{main/transition.png}
	\caption{
		Transition schema of water governance during transformation towards a hydrosocial water cycle. The natural water cycle dominates blue pathways while socio-economic feedback dominate red pathways. Finally, there is a transformation towards the hydrosocial water cycle where red loop increases.
		\textbf{A. Early phase.} As socio-economic systems develop, industry and services gradually demand increasing amounts of water; at the same time, increasing social organization and technological capacity allow people to manage water resources more intensively, including intensive intervention in the natural water cycle.
		\textbf{B. Late phase} With further developed and economically efficient industries and services, trade-offs between provisioning-purpose and non-provisioning water use become prominent. Rather than being determined by local socio-economic systems, water withdraws and management are scaled up to the entire basin.
		%! The note to C. makes no sense! from the refree 2.
		Thus, \textbf{C. Transformation from a natural water cycle towards the hydro-social water cycle} occurs in paralleled with a transformation towards a hydrosocial water cycle. This is generally distinguished when it reaches water resource limits. The three water governance regimes seen in the YRB are identified along this transition (Regime 1: massive supply regime, Regime 2: purpose-focused regime, Regime 3: many-sided governance regime).
		\textbf{D. Water governance challenges} Through the transitional regimes, water governance faces primarily economic and environmental challenges in the early phase and social and policy challenges in the late phase.
	}
	\label{fig:summary}
\end{figure*}

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
Our results show that there have been three distinct but sequential governance regimes within the YRB: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and a demand regulating regime (P3: 2002-2013).
Furthermore, shifts between these regimes were caused by different environmental, economic, social or political drivers, deciding who gets water, when and how.
The process echoes how social systems can change water governance regimes by enhancing their adaptive capacity. %! citation
However, the IWGI quantitatively identifies and reveals that abstract pattern, thus characterizing the transition of water governance in detail for the first time.
It is important to note that each indicator or cause changes gradually, but emerging regime shifts move water governance along with the hydrosocial water cycle at a basin scale.
As a result, the water governance challenges were primarily economic and environmental at the beginning of the trajectory and social and policy-related towards the end (Figure~\ref{fig:summary} C and D).

@@

The start of the governance transforming regime (P2: 1979-2001) coincided with the rising competition for water use after ``opening and reform''.
% 正如理论预测的那样
The results in the YRB keep in line with the suggestions from the theoretical analysis: continuous increases in water demand when the basinal total supply is stable can follow substantial changes in governance regime and the rapid enhancement in overall social adaptive capacity %! Citation.
% 作为制度转变的先行者
Being a pioneer in shifting governing institutions, the YRB triggered a series of changes in ``who gets water, when and how'' during this regime: slowing growth of irrigated acreage; leading water-saving infrastructure; China's first water quota scheme; The preliminary cross-boundaries water transfer plan and so on
\cite{wangThirtyYearsYellow2018}.
% 因此，1999年黄河的最后一次枯竭
Consequently, though water stress remained and increased (mainly led by reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 added a footnote to the climax of this transformation in water governance.

>>>>

\begin{figure*}[htbp!]
	\centering
	\includegraphics[width=0.9\linewidth]{main/transition.png}
	\caption{
		Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways while socio-economic feedback dominate red pathways.
		\textbf{A. Early phase.} As socio-economic systems developing, non-provisioning water demand increases; simultaneously, increased adaptive capacity by engineering allows people to manage water resources for alleviating the water stress.
		\textbf{B. Late phase} With further human interventions, trade-offs between provisioning-purpose and non-provisioning water use become prominent; basin-wide socio-economic system requires to more organized water governance.
		%! The note to C. makes no sense! from the refree 2.
		Thus, \textbf{C. the hydrosocial water cycle transition} correlates with the water governance regime shifts (in the YRB, they are identified as massive supply regime, transformation governance regime, and adaptation oriented regime). The transformation governance regime shift occurs following water deficit, with rapid growth of adaptive capacity.
		\textbf{D. Water governance challenges} Through the transitional regimes, water governance faces primarily economic and environmental challenges in the early phase and social and policy challenges in the late phase.
	}
	\label{fig:summary}
\end{figure*}

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
Our results show that there have been three distinct but sequential governance regimes within the YRB: a massive supply regime (P1: 1965-1978), a governance transforming regime (P2: 1979-2001) and an adaptation oriented regime (P3: 2002-2013).
Furthermore, shifts between these regimes were caused by different environmental, economic, social or political drivers, deciding who gets water, when and how.
The process echoes how social systems can change water governance regimes by enhancing their adaptive capacity. %! citation
However, the IWGI quantitatively identifies and reveals that abstract pattern, thus characterizing the transition of water governance in detail for the first time.
It is important to note that each indicator or cause changes gradually, but emerging regime shifts move water governance along with the hydrosocial water cycle at a basin scale.
As a result, the water governance challenges were primarily economic and environmental at the beginning of the trajectory and social and policy-related towards the end (Figure~\ref{fig:summary} C and D).

@@

The start of the governance transforming regime (P2: 1979-2001) coincided with the rising competition for water use after the ``reform and opening-up''.
% 正如理论预测的那样
The results in the YRB keep in line with the suggestions from the theoretical analysis: continuous increases in water demand when the basinal total supply is stable can follow substantial changes in governance regime and the rapid enhancement in overall social adaptive capacity %! Citation.
% 作为制度转变的先行者
Being a pioneer in shifting governing institutions, the YRB triggered a series of changes in ``who gets water, when and how'' during this regime: slowing growth of irrigated acreage; leading water-saving infrastructure; China's first water quota scheme; The preliminary cross-boundaries water transfer plan and so on
\cite{wangThirtyYearsYellow2018}.
% 因此，1999年黄河的最后一次枯竭
Consequently, though water stress remained and increased (mainly led by reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 added a footnote to the climax of this transformation in water governance.

### 2022-04-26 paper/main/manuscript.tex
docs(abstract,-introduction,-results,-discussion): fit to the new structure and results
BREAKING CHANGE:

\abstract{The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. Authors are advised to check the author instructions for the journal they are submitting to for word limits and if structural elements like subheadings, citations, or equations are permitted.}

\keywords{keyword1, Keyword2, Keyword3, Keyword4}

>>>>

\abstract{
    In many large river basins, transition of water governance regimes from natural to social-ecological or ‘hydrosocial’ situations profoundly changes who gets water, when, and how. Identifying changes of governance regimes is therefore critical to understanding the transition and guiding the efficient and sustainable use of water. We combined three main dimensions of water governance (supply, purpose and allocation) to develop a quantitative Integrated Water Governance Index (IWGI) that can detect regime shifts in water governance at a basin scale. Applying the index to a rapidly-changing large river basin (the Yellow River Basin, China), it describes how water governance shifts between three regimes over half a century (massive supply regime; governance transformation regime; and adaptation oriented regime, respectively). Our application of the IWGI offers a comprehensive and straightforward way to link the shifts of water governance to environmental, economic social and political factors. As a potentially widespread transition schema for water governance regimes, the different governance challenges that occurred at different phases of the transition of the Yellow River also suggest potentially useful guidelines on the coordinated governance of big river basins in general.
}

\keywords{
    Regime shifts,
    Water governance,
    Transformation,
    Sustainability
}
